Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2021-01-20 ms/ms.tex
add trace plots

The posterior distribution of the model parameters $P(\theta \mid \vec{X})$ is estimated using the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC)~\citep{Goodman2010} implemented in the \texttt{emcee} Python package~\citep{Foreman-Mackey2013}. We used the default configuration using the stretch move with stretch scale parameter $a=2$.
For the main analysis we use 50 chains (or walkers) per region, with 7M samples per chain (no thinning was applied).
% TODO add refs and values
The \emph{integrated autocorrelation time}~\citep{Foreman-Mackey2013,Goodman2010} was averaged across parameters and chains for each region. 
It was found to be between XXX for Norway and XXX for Germany (\autoref{fig:autocorr}). % TODO this gives effective number of samples...
We examined the trace plots for $\tau$ in all regions (FIGURE).
All chains seem to converge to the same stationary distribution, in most cases before 2M steps. Thus, we discarded the first 2M samples as burnin samples.
The only exception is Spain, in which a single chain converged at around X steps.
We considered this chain as part of the burnin and removed it from the analysis.
We also ran additional chains with 2M samples and a different initialization (i.e. seed). The estimated posterior distributions of $\tau$ were very similar to our main analysis, further increasing our confidence in the convergence of our inference.
We also examined the joint posterior distributions of $\tau$ and $\lambda$ to check for correlations (FIGURE). %TODO what do we find?

@@

>>>>

The posterior distribution of the model parameters $P(\theta \mid \vec{X})$ is estimated using the affine-invariant ensemble sampler for Markov chain Monte Carlo (MCMC)~\citep{Goodman2010} implemented in the \texttt{emcee} Python package~\citep{Foreman-Mackey2013}. We used the default configuration using the stretch move with stretch scale parameter $a=2$.
For the main analysis we use 50 chains (or walkers) per region, with 7M samples per chain (no thinning was applied).
% TODO add refs and values
The \emph{integrated autocorrelation time}~\citep{Foreman-Mackey2013,Goodman2010} was averaged across parameters and chains for each region. 
It was found to be between XXX for Norway and XXX for Germany (\autoref{fig:autocorr}). % TODO this gives effective number of samples...
We examined the trace plots for $\tau$ in all regions (\autoref{fig:trace}).
All chains seem to converge to the same stationary distribution, in most cases before 2M steps. Thus, we discarded the first 2M samples as burnin samples.
The only exception is Spain, in which a single chain converged at around X steps.
We considered this chain as part of the burnin and removed it from the analysis.
We also ran additional chains with 2M samples and a different initialization (i.e. seed). The estimated posterior distributions of $\tau$ were very similar to our main analysis, further increasing our confidence in the convergence of our inference.
We also examined the joint posterior distributions of $\tau$ and $\lambda$ to check for correlations (FIGURE). %TODO what do we find?

@@

%%% Fig Trace plots
%%% Fig PPC
% TODO update fixed, Wuhan
% generated with ppc.sh
\begin{figure}[p]	
    \centering
    \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Austria_trace3.png}
    \end{subfigure}
    ~%%%
    \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Belgium_trace3.png}
    \end{subfigure}
    ~%%%
    \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Denmark_trace3.png}
    \end{subfigure}
	~%%%
    \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/France_trace3.png}
    \end{subfigure}
    ~%%%
    \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Germany_trace3.png}
    \end{subfigure}
    ~%%% 
    \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Italy_trace3.png}
    \end{subfigure}
    ~%%% 
	\begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Norway_trace3.png}
    \end{subfigure}
    ~%%%  
	\begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Spain_trace3.png}
    \end{subfigure}
    ~%%%
	\begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Sweden_trace3.png}
    \end{subfigure}
    ~%%%  
	\begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Switzerland_trace3.png}
    \end{subfigure}
    ~%%%  
	\begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/United_Kingdom_trace3.png}
    \end{subfigure}
    ~%%%  
	\begin{subfigure}{0.32\textwidth}
        \includegraphics[width=\textwidth]{../figures/traces/Wuhan_trace3.png}
    \end{subfigure}
    \caption{    % TODO update according to requests from Ilia Jan 20 email
    \textbf{Trace plots for $\tau$.}
    The value of $\tau$ at each iteration (i.e. sample or step) of 50 chains per region. Each chain is plotted with a different color. In France and Austria some chains converged relatively late but before the burn-in period (2M iterations). In Spain, a single chain converged very late (after roughly 6M iterations). This chain was removed from further analysis. The y-axis range is set to the support of the prior on $\tau$.
    }
    \label{fig:trace}	    
\end{figure}

% TODO tau-lambda density plots
